Oasis or Mirage? \\ Trade Network Propagation of Deforestation

### 2024-01-02 paper/main.tex
write literature review

@@

\section{Russia and Myanma's Restriction Policy}

@@

\section{identification Strategy}

>>>>

Using annual trade flow and production data of forestry industries, I employ shift-share design to empirically demonstrate effects of supply shock triggered by the ban of log exports. I regress outcome of each country on how much the country is exposed to the supply shock. The exposure to the shock is measured with interaction of two parts. The first part called ``shift'' is a measure of how much export-restricting country reduces their export to the rest of the world with the restriction. The second part called ``share'' is a measure of how much each country has been dependent on a specific market or industry before the restriction. Combining these two parts, we obtain measure of how much each country is exposed to the Russia or Myanmar's export restriction policy. By using this shift-share approach, I find that when log export restrictions are imposed in a country, log production increases in the country with the larger exposure to that supply shock, i.e., the country that was the export-restricting country's major export destination. This indicates that a country's log export restrictions contribute to deforestation in its major trading partners. On the other hand, for countries that exported to markets similar to that export-restricting country, there was no significant response in terms of production, export volume, or export value to the export-restriction shock. These results suggest that an pro-environmental policy in one country to protect its own forest has effect to propagate deforestation to their previous trade partners. This implicates that an efficacy of one country's forest protection can be crowded out by the spillover effects. It emphasizes that one government policy to protect its own forest is not sufficient to tackle with global environmental issue.\\

Although a large number of previous studies have discussed economics of deforestation, most studies have focused on relationship between policy interventions and deforestation within one country. For example, \cite{burgess2012political} describes how increase in political jurisdictions cause deforestation in Indonesia. \cite{abman2020does} discusses not only mechanism in which access to the timber markets increases log production but also mechanism in which trade openness to the agricultural market affects people's decision on land usage. \cite{harstad2023contingent} explains how trade agreement affects firms' decision on how much they exploit the forests. Nevertheless, the previous literature has not figured out how one country's policy to reduce deforestation propagates deforestation to the other countries through international trade. \\

On the other hand, literature of environment economics has studies how trade propagates environmental pollution is ``exported'' from developed countries to developing countries as ``pollution heaven hypothesis''. Since developed countries are more strict on firms' pollution of their neighboring environment than developing countries, firms often relocate factories which emit pollution materials from developed countries to developing countries. For example, \cite{hanna2010us} demonstrates that US regulation on firms' air pollution caused regulated multinational firms to increase their foreign output and foreign assets. \cite{tanaka2022north} examines effect of US air quality standard on relocation of battery recycling factories to Mexico and on infant health in Mexico. As these paper discusses, pro-environmental regulation in one country may propagate environmental issue to the other countries. \\

This paper contributes to fill the gap between literature on deforestation and that on pollution heaven hypothesis by empirically shows trade network propagates deforestation with one country's regulation. This study will provide critical evidence in discussing how to solve the issue of deforestation. That is because it is necessary to globally maintain forests and increase how much carbon dioxide can be absorbed in a global scale when we tackle international environment issue such as climate change. Protection of forests in one country at the expense of another country's forest does not contribute to reduction in global carbon dioxide. The results of this paper emphasizes this important implication. \\

As for the empirical method to examine propagation of a supply shock, I refer to recent growing literature of network analysis in economics. Acemoglu firstly introduces the analysis of how shock on an agent propagates to the other agents throughout network between agents. Based on this strand, various papers discuss how a shock to a specific firms affects the other firms that do not directly suffer from the shock through production supply chain. For example, \cite{barrot2016input} and \cite{carvalho2021supply} examine how shocks of the Eastern Japan Great Earthquake affects firms that are located far from the damaged area through their supply chain networks. I follow shift-share approach of \cite{huneeus2018production} to empirically show the network propagation effects of one country's pro-environmental policy on the other countries.\\

@@

\section{Russia and Myanmar's Restriction Policy}

@@

\section{Identification Strategy}
